---
title: "Replace `NA` with `1` and keep items with over 20% `NA` answers "
author: "Mingyang Cai"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---
  
<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

# Packages used
The following packages are used.  
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation  
library(mice)     # Data imputation  
library(magrittr) # Pipes  
library(purrr)    # Functional programming  
library(ggplot2)  # Plotting device  
library(lavaan)   # Latent variable analysis  
library(psych)    # Factor analysis  
library(polycor)  # Polychoric correlation  
library(GPArotation) #Rotation 
```

---

# Read in the data file
We load all workspaces from the `\Workspaces\` directory in the project's root.
```{r}
load("../../../Workspaces/1. Data import and preparation.Rdata")
load("../../../Workspaces/2. Data inspection.Rdata")
load("../../../Workspaces/3. Data imputation.Rdata")
load("../../../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Setting the RNG seed
```{r}
set.seed(123)
```

---

# Combine two dichotomous misconduct items (`RRfabr` and `RRfals`) 
```{r}
d50 <- d50 %>% 
  map(~.x %>% 
        mutate(RR_sum = rowSums(cbind(RRfabr, RRfals))))
```

---

# Test the model with one factor
```{r}
Model.1 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QNoReSubmit + QConcealFlaws + QSelectCites         
                 + RDisclFunds + RCorrectPub + RAuthorship + ROpenData 
                 + RKeepRecord + RPreReg + RDataManage + ROpenAccess 
                 + RCiteSource + ROpenCode + RErrorCheck           
                 + RR_sum  
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RCorrectPub ~~ RErrorCheck
            ROpenData ~~ ROpenCode
'
fit.model.1 <- cfa(Model.1, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.1, fit.measures = TRUE)
```
The CFI is much less than 0.9.

---

# Test the model with two factors
```{r}
Model.2 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QNoReSubmit + QConcealFlaws + QSelectCites 
                 + RR_sum
            RRP =~ RDisclFunds + RCorrectPub + RAuthorship + ROpenData 
                 + RKeepRecord + RPreReg + RDataManage + ROpenAccess 
                 + RCiteSource + ROpenCode + RErrorCheck 
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RCorrectPub ~~ RErrorCheck
            ROpenData ~~ ROpenCode 

'
fit.model.2 <- cfa(Model.2, data = complete(d50[[1]]), estimator = "WLSMV", std.lv=TRUE)
summary(fit.model.2, fit.measures = TRUE)

```
The CFI is 0.83. 

---

# Five modifications to improve Model 2
```{r}
modificationindices(fit.model.2, sort. = TRUE, maximum.number = 5)
Model.2.modi <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QNoReSubmit + QConcealFlaws + QSelectCites 
                 + RR_sum
                 + RErrorCheck + RCiteSource
            RRP =~ RDisclFunds + RCorrectPub + RAuthorship + ROpenData 
                 + RKeepRecord + RPreReg + RDataManage + ROpenAccess 
                 + RCiteSource + ROpenCode + RErrorCheck 
                 + QNoReSubmit + QConcealFlaws
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RCorrectPub ~~ RErrorCheck
            ROpenData ~~ ROpenCode 
            QCiteSource ~~   RCiteSource

'
fit.model.2.modi <- cfa(Model.2.modi, data = complete(d50[[1]]), estimator = "WLSMV", std.lv=TRUE)
summary(fit.model.2.modi, fit.measures = TRUE)
```
The CFI now is 0.89. 


---
 
# Investigate the model with three factors by explanatory factor analysis
```{r}
data.for.fa <- complete(d50[[1]])[c(105:126, 140)]
#hetcor(data.for.fa, ML = TRUE)$correlations

fafit.free <- complete(d50[[1]]) %>% extract(c(105:126, 140)) %>% hetcor(ML = TRUE) %>% use_series(correlations) %>% fa(., nfactors = 23, rotate = "none")
n.factors <- length(fafit.free$e.values)
#data.frame(factor.num = as.factor(1 : length(fafit.free$e.values)),
#           Eigenvalue = fafit.free$e.values) %>% ggplot(aes(x = factor.num, 
#                                                            y = Eigenvalue, 
#                                                            group = 1)) + 
#  geom_point() + geom_line() + xlab("Number of factors") + 
#  ylab("Initial eigenvalue") + ggtitle("Scree plot")

efa.fit.3 <- complete(d50[[1]]) %>% extract(c(105:126, 140)) %>% hetcor(ML = TRUE) %>% use_series(correlations) %>% fa(., nfactors = 3, rotate = "promax")
#print(efa.fit.3)
fa.diagram(efa.fit.3)
```

The factor path plot shows the structure of the model with three factors.

---

# Perform confirmatory factor analysis with three factors
```{r}
Model.3 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QNoReSubmit + QConcealFlaws + QSelectCites 
                 + RR_sum
            RRP.1 =~ RDisclFunds + RCorrectPub + RAuthorship  + ROpenAccess 
                   + RCiteSource  + RErrorCheck 
            RRP.2 =~ RKeepRecord + RDataManage + ROpenData + ROpenCode     
                   + RPreReg
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RCorrectPub ~~ RErrorCheck
            ROpenData ~~ ROpenCode 
            RRP.1 ~~ RRP.2
            QRP ~~ RRP.1
            QRP ~~ RRP.2

'
fit.model.3 <- cfa(Model.3, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.3, fit.measures = TRUE)

```
The CFI is 0.84, which shows the model with three factors does not improve the result notably.

---

# Five modifications to improve Model 3
```{r}
modificationindices(fit.model.3, sort. = TRUE, maximum.number = 5)

Model.3.modi <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QNoReSubmit + QConcealFlaws + QSelectCites 
                 + RR_sum
                 + RErrorCheck
            RRP.1 =~ RDisclFunds + RCorrectPub + RAuthorship  + ROpenAccess 
                   + RCiteSource  + RErrorCheck 
                   + QNoReSubmit
            RRP.2 =~ RKeepRecord + RDataManage + ROpenData + ROpenCode     
                   + RPreReg
                   + QNoReSubmit + QConcealFlaws
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RCorrectPub ~~ RErrorCheck
            ROpenData ~~ ROpenCode 
            RRP.1 ~~ RRP.2
            QRP ~~ RRP.1
            QRP ~~ RRP.2
            QCiteSource ~~   RCiteSource

'
fit.model.3.modi <- cfa(Model.3.modi, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.3.modi, fit.measures = TRUE)

```
The CFI is now 0.892.
