---
title: "Part 5-How many factors-9"
author: "Mingyang Cai"
date: ""
output: 
   html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: false
---
  
<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

Part 5: Structural equation model (MIMIC SEM) How many factors?  
Replace 1 for the 0 scores (Not Applicable) in the raw RRP/QRP variables and remove 3 RRPs (`RCorrectPub`, `RPreReg` and `ROpenCode`) and 1 QRP (`QNoReSubmit`) whose percentages of `NA` answers exceed 20%. 

---

# Packages used
The following packages are used.  
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation  
library(mice)     # Data imputation  
library(magrittr) # Pipes  
library(purrr)    # Functional programming  
library(ggplot2)  # Plotting device  
library(lavaan)   # Latent variable analysis  
library(psych)    # Factor analysis  
library(polycor)  # Polychoric correlation  
library(GPArotation) #Rotation   
```

---

# Read in the data file
I load all workspaces from the `\Workspaces\` directory in the project's root.
```{r}
load("../Workspaces/1. Data import and preparation.Rdata")
load("../Workspaces/2. Data inspection.Rdata")
load("../Workspaces/3. Data imputation.Rdata")
load("../Workspaces/5. Preparation Imputed Datasets.Rdata")
```

---

# Setting the RNG seed
```{r}
set.seed(123)
```

---

# Combine two dichotomous misconduct items (`RRfabr` and `RRfals`) 
```{r}
d50 <- d50 %>% 
  map(~.x %>% 
        mutate(RR_sum = rowSums(cbind(RRfabr, RRfals))))
RRP <- c("RDisclFunds", "RAuthorship", "ROpenData", "RKeepRecord",
         "RDataManage", "ROpenAccess", "RCiteSource", "RErrorCheck")
QRP <- c("QAttention", "QSupervision", "QResDesign", "QUnfairRev", "QUnsubstClaims", 
         "QCiteSource", "QResNotes", "QConcealDetails", "QConcealFlaws", "QSelectCites")


d50 <- d50 %>% 
  map(select, -RCorrectPub_raw, -RPreReg_raw, -ROpenCode_raw, -QNoReSubmit_raw,
              -RCorrectPub, -RPreReg, -ROpenCode, -QNoReSubmit)
```

---

# Test the model with one factor
```{r}
Model.1 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites         
                 + RDisclFunds + RAuthorship + ROpenData 
                 + RKeepRecord + RDataManage + ROpenAccess 
                 + RCiteSource + RErrorCheck           
                 + RR_sum  
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
'
fit.model.1 <- cfa(Model.1, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.1, fit.measures = TRUE)
```
CFI is 0.55.

---

# Five modifications to improve Model 1
```{r}
modificationindices(fit.model.1, sort. = TRUE, maximum.number = 5)

Model.1.modi <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites         
                 + RDisclFunds + RAuthorship + ROpenData 
                 + RKeepRecord + RDataManage + ROpenAccess 
                 + RCiteSource + RErrorCheck           
                 + RR_sum  
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RKeepRecord ~~ RDataManage
            RDisclFunds ~~ ROpenAccess
            ROpenData ~~ ROpenAccess
            ROpenData ~~ RKeepRecord
            ROpenData ~~ RDataManage
            
'
fit.model.1.modi <- cfa(Model.1.modi, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.1.modi, fit.measures = TRUE)

```
CFI increases to 0.69.

---

# Test the model with two factors
```{r}
Model.2 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites 
                 + RR_sum
            RRP =~ RDisclFunds + RAuthorship + ROpenData 
                 + RKeepRecord + RDataManage + ROpenAccess 
                 + RCiteSource + RErrorCheck 
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship

'
fit.model.2 <- cfa(Model.2, data = complete(d50[[1]]), estimator = "WLSMV", std.lv=TRUE)
summary(fit.model.2, fit.measures = TRUE)
```
The CFI is 0.85.

---

# Five modifications to improve Model 2
```{r}
modificationindices(fit.model.2, sort. = TRUE, maximum.number = 5)

Model.2.modi <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites 
                 + RR_sum + RDisclFunds
            RRP =~ RDisclFunds + RAuthorship + ROpenData 
                 + RKeepRecord + RDataManage + ROpenAccess 
                 + RCiteSource + RErrorCheck + QConcealFlaws
                 + QCiteSource
                 
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RKeepRecord ~~   RDataManage
            QCiteSource ~~   RCiteSource

'
fit.model.2.modi <- cfa(Model.2.modi, data = complete(d50[[1]]), estimator = "WLSMV", std.lv=TRUE)
summary(fit.model.2.modi, fit.measures = TRUE)
```
The CFI now is 0.91. 

---
 
# Investigate model with three factors with explanatory factor analysis
```{r}
efa.fit.3 <- complete(d50[[1]]) %>% extract(c(101:118, 132)) %>% hetcor(ML = TRUE) %>% use_series(correlations) %>% fa(., nfactors = 3, rotate = "promax")
print(efa.fit.3)
fa.diagram(efa.fit.3)
```

The factor path plot shows the structure of the model with three factors. `MR1` is the QRP factor, `MR2` is one RRP factor (RRP.1) and `MR3` is the other RRP factor (RRP.2). 

---

# Perform confirmatory factor analysis with three factors
```{r}
Model.3 <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites 
                 + RR_sum
            
            RRP.1 =~ RCiteSource + ROpenAccess + RDisclFunds + RAuthorship
                   + RErrorCheck + ROpenData
                   
            RRP.2 =~ RKeepRecord + RDataManage       
            
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RRP.1 ~~ RRP.2

'
fit.model.3 <- cfa(Model.3, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.3, fit.measures = TRUE)
```
The CFI is 0.86.

---

# Five modifications to improve Model 3
```{r}
modificationindices(fit.model.3, sort. = TRUE, maximum.number = 5)
Model.3.modi <- '#latent variable definition
            QRP =~ QAttention + QSupervision + QResDesign + QUnfairRev 
                 + QUnsubstClaims + QCiteSource + QResNotes + QConcealDetails 
                 + QConcealFlaws + QSelectCites 
                 + RR_sum + RDisclFunds
            
            RRP.1 =~ RCiteSource + ROpenAccess + RDisclFunds + RAuthorship
                   + RErrorCheck + ROpenData + QConcealFlaws + QCiteSource
                   
            RRP.2 =~ RKeepRecord + RDataManage + QConcealFlaws      
            
            #variance and covariance
            RDisclFunds ~~ RAuthorship
            RRP.1 ~~ RRP.2
            QCiteSource ~~ RCiteSource

'
fit.model.3.modi <- cfa(Model.3.modi, data = complete(d50[[1]]), estimator = "WLSMV")
summary(fit.model.3.modi, fit.measures = TRUE)
```
The CFI is now 0.91.
